Simulation Comparison

### 2020-12-04 output_scripts/Paper_Plots.Rmd
update rank sim fits to include them in same simulation script.
also examining the structure score

@@

```{r load rankings,echo=FALSE,include=FALSE,results='hide',cache=TRUE}
full_data <- readRDS("../data/mice.RData")
# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
cut_off <- 3
mice_number <- 12

@@

# Figure 5b: Simulation Spearman Rank
```{r fig-5b-spearman-sim, fig.height=7}
sim_files <- list.files(here("output", "rank_sims",
                             "sims_m3_dc_isi_sparse"))

@@

  m3_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                       "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))
  if(length(prob_id) != 0) {
    m3_pr <- m3_pr[-prob_id,-prob_id]
  }
  indep_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                       "/immhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))
  # print(range(as.vector(indep_pr)))
  if(length(prob_id) != 0) {
    indep_pr <- indep_pr[-prob_id,-prob_id]
  }
  if(current_cohort == 10) {
    # one additional row
    # print("in here")
    new_prob_row <- which(rowSums(m1_pr) == 0)
    new_prob_col <- which(colSums(m1_pr) == 0)
    prob_id <- c(new_prob_row,new_prob_col) 
    if(length(prob_id) != 0) {
      m1_pr <- m1_pr[-prob_id, -prob_id]
      m2_pr <- m2_pr[-prob_id, -prob_id]
      m3_pr <- m3_pr[-prob_id, -prob_id]
      indep_pr <- indep_pr[-prob_id, -prob_id]
    }
  }

  m1_score <-positiveNegativeApproxError(m1_pr)
  m2_score <- positiveNegativeApproxError(m2_pr)
  m3_score <- positiveNegativeApproxError(m3_pr) ## smallest value which is good
  ind_score <- positiveNegativeApproxError(indep_pr) 
  ## this doesn't make sense because all negative
  ## values
  current_score <- tibble(m1_score, m2_score, m3_score, ind_score)
  names(current_score) <- c("C-HP","C-DCHP","C-MMHP","I-MMHP")
  current_score$type <- c("Positive Residuals","Negative Residuals")
  current_score$Cohort <- current_cohort
  struct_scores <-struct_scores %>% bind_rows(current_score)
}

struct_plot <- struct_scores %>% 
  rename(Pos_Neg = type) %>%
  pivot_longer(cols = "C-HP":"I-MMHP",
               names_to = "Method", values_to = "Score") %>%
  filter(Score > 0) %>%
  filter(!(Method == "I-MMHP" & Pos_Neg == "Positive"))
  # mutate(Method = as.factor(Method, levels = c("I-MMHP","C-HP","C-DCHP",
  #                                              "C-MMHP"))) %>%
struct_plot$Method <- factor(struct_plot$Method, levels = c("I-MMHP","C-HP","C-DCHP",
                                               "C-MMHP") )

box_cols <- col_df %>% 
  filter(method %in% c("I-MMHP","C-HP","C-DCHP","C-MMHP")) %>%
  pull(cols)

struct_plot %>% 
  ggplot(aes(Method,Score, fill = Method)) + geom_boxplot() + 
  scale_fill_manual(values = box_cols) +
  ggtitle("(b)") +
  facet_wrap(~Pos_Neg) + theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
              text = element_text(size = 20),
              axis.text.y =element_text(size = 11),
              axis.text.x = element_blank(),
              axis.title.x=element_blank() )

@@

```{r fig-8a-frob-norm-cohort5, fig.width=8,fig.height=4}
load("../output/plot_N_predict.RData")
current_cohort <- 5# cohort 1 looks worse than rest

@@

```{r fig-8b-frob-norm-all-cohorts,fig.width=8,fig.height=4}
load("../output/plot_N_predict.RData")
temp_plot_df <- all_cohort_norm_df %>% 
  group_by(day, method) %>% 
  summarise(avg=mean(norm), n= n(), sd=sd(norm))

@@

```{r fig-8b-frob-norm-boxplot, fig.width=8, fig.height=4}
load("../output/plot_N_predict.RData")

@@

all_cohort_box %>% 
  ggplot(aes(x=method,y=norm, fill = method)) +
  # facet_grid(cols = vars(day)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  ggtitle("(b)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  # guides(color=guide_legend(title="Method")) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") +
  labs(fill = "Method") +
  # ylim(0, 80) +
  NULL

@@

```{r fig-9a-spearman-rank-cohort1}
load(here("output","plot_rank_predict.RData"))
# current_cohort <- 5
temp_plot_df <- predict_day_rank_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP",
                                         "C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
# png(paste(plot_path,"real_predict_rank_one_cohort.png",sep=""),
# width=600,height=300)
p5 <- ggplot(temp_plot_df, aes(x = method, y = spearman, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  #scale_fill_manual(values =
  # c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) + 
  ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(), 
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Spearman rank correlation") +
  # ylim(0, 1) +
  NULL
p5 + labs(fill = "Method")
```

@@

```{r fig-9b-spearman-rank-all-cohorts}
load("../output/plot_rank_predict.RData")
temp_plot_df <- all_cohort_rank_df %>% 
  group_by(day, method) %>% 
  summarize(avg=mean(spearman), n= n(), sd=sd(spearman))

>>>>

cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
cut_off <- 3
mice_number <- 12

@@

```{r load rankings,echo=FALSE,include=FALSE,results='hide',cache=TRUE}
full_data <- readRDS("../data/mice.RData")
# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45

@@

# Figure 5b: Simulation Spearman Rank
```{r fig-5b-spearman-sim, fig.height=7}
sim_files <- list.files(here("output", "sims_m3_update",
                             "sims_m3_dc_isi_sparse"))

@@

  m3_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                       "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))
  if(length(prob_id) != 0) {
    m3_pr <- m3_pr[-prob_id,-prob_id]
  }
  indep_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                       "/immhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))
  # print(range(as.vector(indep_pr)))
  if(length(prob_id) != 0) {
    indep_pr <- indep_pr[-prob_id,-prob_id]
  }
  if(current_cohort %in% c(8,10)) {
    # one additional row
    # print("in here")
    new_prob_row <- which(rowSums(m1_pr) == 0)
    new_prob_col <- which(colSums(m1_pr) == 0)
    prob_id <- c(new_prob_row,new_prob_col) 
    if(length(prob_id) != 0) {
      m1_pr <- m1_pr[-prob_id, -prob_id]
      m2_pr <- m2_pr[-prob_id, -prob_id]
      m3_pr <- m3_pr[-prob_id, -prob_id]
      indep_pr <- indep_pr[-prob_id, -prob_id]
    }
  }

  m1_score <-positiveNegativeApproxError(m1_pr)
  m2_score <- positiveNegativeApproxError(m2_pr)
  m3_score <- positiveNegativeApproxError(m3_pr) ## smallest value which is good
  ind_score <- positiveNegativeApproxError(indep_pr) 
  ## this doesn't make sense because all negative
  ## values
  current_score <- tibble(m1_score, m2_score, m3_score, ind_score)
  names(current_score) <- c("C-HP","C-DCHP","C-MMHP","I-MMHP")
  current_score$type <- c("Positive Residuals","Negative Residuals")
  current_score$Cohort <- current_cohort
  # current_score$resids <- list(m1 = m1_pr,
  #                              m2 = m2_pr,
  #                              m3 = m3_pr,
  #                              ind = indep_pr)
  struct_scores <-struct_scores %>% bind_rows(current_score)
}

struct_plot <- struct_scores %>% 
  rename(Pos_Neg = type) %>%
  pivot_longer(cols = "C-HP":"I-MMHP",
               names_to = "Method", values_to = "Score") 
  # filter(Score > 0) %>%
  # filter(Score < 0.99) %>%
  # filter(!(Method == "I-MMHP" & Pos_Neg == "Positive"))
  # mutate(Method = as.factor(Method, levels = c("I-MMHP","C-HP","C-DCHP",
  #                                              "C-MMHP"))) %>%
struct_plot$Method <- factor(struct_plot$Method, levels = c("I-MMHP","C-HP","C-DCHP",
                                               "C-MMHP") )

# box_cols <- col_df %>% 
#   filter(method %in% c("I-MMHP","C-HP","C-DCHP","C-MMHP")) %>%
#   pull(cols)

struct_plot %>% 
  ggplot(aes(Method,Score, fill = Method)) + geom_boxplot() + 
  # scale_fill_manual(values = box_cols) +
  ggtitle("(b)") +
  facet_wrap(~Pos_Neg) + theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
              text = element_text(size = 20),
              axis.text.y =element_text(size = 11),
              axis.text.x = element_blank(),
              axis.title.x=element_blank() )

@@

```{r fig-8a-frob-norm-cohort5, fig.width=8,fig.height=4,eval=FALSE}
load("../output/plot_N_predict.RData")
current_cohort <- 5# cohort 1 looks worse than rest

@@

```{r fig-8b-frob-norm-all-cohorts,fig.width=8,fig.height=4, eval=FALSE}
load("../output/plot_N_predict.RData")
temp_plot_df <- all_cohort_norm_df %>% 
  group_by(day, method) %>% 
  summarise(avg=mean(norm), n= n(), sd=sd(norm))

@@

```{r fig-7-pred-all-cohorts-box, fig.width=8, fig.height=4}
load("../output/plot_N_predict.RData")

@@

all_cohort_box %>% 
  ggplot(aes(x=method,y=norm, fill = method)) +
  # facet_grid(cols = vars(day)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  # guides(color=guide_legend(title="Method")) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") +
  labs(fill = "Method") +
  # ylim(0, 80) +
  NULL

@@

```{r fig-9a-spearman-rank-cohort1, eval=FALSE}
load(here("output","plot_rank_predict.RData"))
# current_cohort <- 5
temp_plot_df <- predict_day_rank_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP",
                                         "C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
# png(paste(plot_path,"real_predict_rank_one_cohort.png",sep=""),
# width=600,height=300)
p5 <- ggplot(temp_plot_df, aes(x = method, y = spearman, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  #scale_fill_manual(values =
  # c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) + 
  ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(), 
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Spearman rank correlation") +
  # ylim(0, 1) +
  NULL
p5 + labs(fill = "Method")
```

@@

```{r fig-7-pred-rank-spearman-all-cohorts}
load("../output/plot_rank_predict.RData")
temp_plot_df <- all_cohort_rank_df %>% 
  group_by(day, method) %>% 
  summarize(avg=mean(spearman), n= n(), sd=sd(spearman))

### 2020-12-04 output_scripts/cmmhp_comparison/sim_comparison.Rmd
update rank sim fits to include them in same simulation script.
also examining the structure score

dc_sim_path <- here::here("output", "sims", "sims_m3_dc")
comm_sim_path <- here::here("output", "common_rate", "sims_m3")
cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')

@@

```{r ks-pr-computation-dc}
object_par <- list(sim_lambda_0 = 0.08,
                   sim_lambda_1 = 0.16,
                   sim_eta_1 = 2.5,
                   gamma_var = c(0.01, 0.02, 0.03, 0.06, 0.07),
                   zeta_var = c(0.075, 0.02, 0.03, 0.05, 0.08),
                   sim_eta_2 = 0.6,
                   sim_eta_3 = 5,
                   sim_beta = 1.5,
                   f_vec_1 = c(0.1, 0.2, 0.4, 0.7, 0.9))

## Iteration on 50 simulations
for(s in c(1:n_sim)){
  load(here(dc_sim_path,paste0("sim_model3_fit123_",s,".RData")))
  load(here(dc_sim_path,paste0("fit123_state_est_",s,".RData",sep='')))
  clean_sim_data <- cleanSimulationData(raw_data=sim_model3_data, 
                                        cut_off = cut_off,
                                        N = length(object_par$f_vec_1))

>>>>

dc_sim_path <- here::here("output", "sims_m3_update")
comm_sim_path <- here::here("output", "common_rate", "sims_m3")
cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')

@@

```{r ks-pr-computation-dc}
object_par <- list(sim_lambda_1 = 0.2,
                   sim_eta_1 = 2.5,
                   gamma_var = c(0.05, 0.02, 0.03, 0.08, 0.01),
                   zeta_var = c(0.075, 0.1, 0.05, 0.01, 0.02),
                   sim_eta_2 = 0.6,
                   sim_eta_3 = 5,
                   sim_beta = 1.5,
                   f_vec_1 = c(0.1, 0.2, 0.4, 0.7, 0.9))

N_array <- array(0, dim = c(n_sim, length(object_par$f_vec_1),
                         length(object_par$f_vec_1))) 
Lambda_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                     length(object_par$f_vec_1))) 
Lambda_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                     length(object_par$f_vec_1)))
Lambda_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                     length(object_par$f_vec_1))) 
Lambda_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                   length(object_par$f_vec_1))) 
PR_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1)))
PR_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1))) 
PR_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1)))
PR_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                               length(object_par$f_vec_1))) 
KS_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1)))
KS_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                 length(object_par$f_vec_1)))
KS_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                    length(object_par$f_vec_1)))
KS_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                               length(object_par$f_vec_1)))
KS_p_model1_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                   length(object_par$f_vec_1)))
KS_p_model2_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                   length(object_par$f_vec_1)))
KS_p_model3_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                    length(object_par$f_vec_1)))
KS_p_true_array <- array(0, dim = c(n_sim,length(object_par$f_vec_1),
                                    length(object_par$f_vec_1)))
current_sims <- 1:n_sim
# 7,31,34,43,47,49
## Iteration on 50 simulations
# 3,8,11,16,19,24,27,41,45,46,48
for(s in 1:n_sim){
  load(here(dc_sim_path,paste0("sim_model3_fit123_",s,".RData")))
  load(here(dc_sim_path,paste0("fit123_state_est_",s,".RData",sep='')))
  clean_sim_data <- cleanSimulationData(raw_data=sim_model3_data, 
                                        cut_off = cut_off,
                                        N = length(object_par$f_vec_1))
